QALY Comparisons - Energy Crisis Interventions

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Remove a line that was left by accident

ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Incidence of Mortality Comparison')

pivot_wider(names_from = 'year',
              values_from = 'dead_pop')
```

>>>>

ggplot(deaths, aes(x = year, y = death_incidence, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Incidence of Mortality Comparison')
```
